\renewcommand{\abstractname}{}
\begin{abstract}
\noindent
%TC:ignore
%TODO THIS NEEDS TO BE REWRITTEN AND PROOF READ (!important).
\textit{
This thesis measures the extent to which courts in Australia draw upon academic literature to form legal precedent. Though courts have long exercised caution in relying on secondary materials, it is speculated that contemporary courts are far more receptive to considering the opinion of legal academics. The relatively modern introduction of secondary material into legal judgments is theorised to largely be driven by the practises of the High Court. As prior literature on this practice runs thin, the following exploratory study treads new ground by exploring the receptivity for citing journal articles to a scope and degree not yet attempted in Australia. In support of the exploratory process, a scientometric framework is introduced that will be applied to a comprehensive dataset of Australian legal opinions spanning 1998 to 2022. This will be followed by a brief overview of the technical aspects of this study, including the use of evaluative algorithms such as discrete-time Markov chains and related concepts founded in linear algebra. The elicited trends will be analysed in part by isolating elements of the results, such as the years and forums. After addressing the method and selected data, critical insights will be drawn on how courts have utilised secondary sources, identifying the academic intuitions, authors, and formats most influential on the development of modern-day law. Concluding remarks on the limitations of this study and possible avenues for future research will complete this study.
}
%TC:endignore
\end{abstract}
